Correct and Secure Web Programming using Dependent Types and Embedded Domain-Specific Languages

### 2013-08-14 paper/main.tex

\begin{abstract}
Dependently-typed languages allow much expressive types to be used within programs, in turn allowing easier reasoning about the operation of such programs. Stronger specifications do however bring with them the disadvantage that it becomes increasingly difficult to write programs that are accepted by the type checker and additional proofs may have to be specified by a user.

>>>>

\begin{abstract}
Dependently-typed languages allow for much expressive types to be used within
programs in turn allowing easier reasoning about the operation of such
programs. Stronger specifications do however bring with them the disadvantage
that it becomes increasingly difficult to write programs that are accepted by
the type checker and additional proofs may have to be specified by a user.
